---
output:
  html_document: default
  pdf_document: default
---
Install the package "babynames"
Plot the number of male and female babies named Taylor *by year*

```{r}
if (!require("babynames")) install.packages("babynames")
if (!require("tidyverse")) install.packages("tidyverse")

library(babynames)

babynames %>% filter(name == "Taylor") %>% arrange(year) %>% ggplot(aes(year, n, color = sex)) + geom_line() +
  xlab("year") +
  ylab("Frequency") +
  ggtitle("Year wise Frequency for the name Taylor for Female & Male")


```
Answer the following questions, showing plots to substantiate your answers (except 4):

1.Is a 23-year old named Quinn more likely to be a boy or a girl?
Ans. The plot has taken into account the survey years where the last year shows 2017 but the babies born in 2017 would be 0 years so we need to consider 2018 instead to account for all 23 year old's named Quinn. Although I have made graphs for both 2017 & 2023. As per the graph the probability of having a Male Quinn is very likely for 23 year olds
```{r}
quinn_23yr2017 <- babynames %>% filter(name == "Quinn" & year == (2018-23)) %>% select(sex, n) %>% ggplot(aes(sex, n)) + geom_col(fill="green") +
  xlab("sex") +
  ylab("Frequency") +
  ggtitle("Sex wise Frequency for the name Quinn at 23years old age.")
quinn_23yr2017

#with 2023 

quinn_23yr2023 <- babynames %>% filter(name == "Quinn" & year == (2023-23)) %>% select(sex, n) %>% ggplot(aes(sex, n)) + geom_col(fill="blue") + 
  xlab("sex") +
  ylab("Frequency") +
  ggtitle("Sex wise Frequency for the name Quinn at 23years old age.")
quinn_23yr2023

```


Is a 6 year old named Quinn more likely to be a boy or a girl?
Ans. The plot has taken into account the survey years where the last year shows 2017 but the babies born in 2017 would be 0 years so we need to consider 2018 instead to account for all 6 year old's named Quinn. Although I have made graphs for both 2017 & 2023. As per the graph the probability of having a Female Quinn is very likely for 6 year olds
```{r}
quinn_6yr2017 <- babynames %>% filter(name == "Quinn" & year == (2018-6)) %>% select(sex, n) %>% ggplot(aes(sex, n)) + geom_col(fill="purple") +
  xlab("sex") +
  ylab("Frequency") +
  ggtitle("Sex wise Frequency for the name Quinn at 6years old age.")
quinn_6yr2017

#with 2023 as year 

quinn_6yr2023 <- babynames %>% filter(name == "Quinn" & year == (2023-6)) %>% select(sex, n) %>% ggplot(aes(sex, n)) + geom_col(fill="yellow")  + 
  xlab("sex") +
  ylab("Frequency") +
  ggtitle("Sex wise Frequency for the name Quinn at 6years old age.")
quinn_6yr2023
```


What is your best guess as to how old a woman named Susan is?
Ans. As per the dataframe and graph we can see that Susan is 63 years old if we consider 2017/18 as last year. If we consider 2023 year it will be 68 years old.
```{r}
susanage <- babynames %>% mutate(age = 2018-year)  %>% filter(name == "Susan" & sex == "F" & age <= 100) %>% arrange(year)

susanage %>% ggplot(aes(age, n)) + geom_line() +
  xlab("Age") +
  ylab("Frequency") +
  ggtitle("Finding Susan's age")
susanage %>% arrange(desc(n))

#with 2023 year

susanage <- babynames %>% mutate(age = 2023-year)  %>% filter(name == "Susan" & sex == "F" & age <= 100) %>% arrange(year)

susanage %>% ggplot(aes(age, n)) + geom_line() +
  xlab("Age") +
  ylab("Frequency") +
  ggtitle("Finding Susan age")

susanage %>% arrange(desc(n))
```
Find the five most popular female names in the year 2017.
Ans.We can see that by simply arranging the data after applying filter we get the five most popular names as: Emma, Olivia, Ava, Isabella and Sophia
```{r}
female_popular <- babynames %>% filter(year == 2017 & sex == "F") %>% arrange(desc(n))
head(female_popular, 5)
```
